Omics-based Single Step Trait Prediction

### 2017-03-16 paper/manuscript.tex
Cosmetic changes to tables and figures

% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Wed Mar 15 17:33:34 2017
% Script: ./analysis/maizego_plot_predictive_abilities.R
\begin{table}[ht]
\centering
\caption{Predictive abilities and corresponding coefficients of variation for the set of 211 tropical/subtropical lines from the maize diversity panel.} 
\begin{tabular}{rllllll}
  \toprule
 & 100grainweight & cobweight & Eardiameter & Kernelwidth & Plantheight & Silkingtime \\ 
  \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: FALSE}}\\
G & 0.43 (0.07) & 0.37 (0.17) & 0.39 (0.05) & 0.34 (0.05) & 0.45 (0.08) & 0.53 (0.03) \\ 
  GT & 0.44 (0.07) & 0.33 (0.17) & 0.4 (0.05) & 0.34 (0.04) & 0.4 (0.07) & 0.53 (0.03) \\ 
   \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: TRUE}}\\
G & 0.36 (0.08) & 0.21 (0.17) & 0.3 (0.05) & 0.34 (0.05) & 0.41 (0.08) & 0.45 (0.03) \\ 
  T & 0.4 (0.07) & 0.15 (0.16) & 0.37 (0.05) & 0.36 (0.04) & 0.32 (0.07) & 0.49 (0.03) \\ 
   \bottomrule
\multicolumn{6}{l}{}\\
\end{tabular}
\end{table}

% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Wed Mar 15 17:31:28 2017
% Script: ./analysis/uhoh_plot_predictive_abilities.R
\begin{table}[ht]
\centering
\caption{Predictive abilities and corresponding coefficients of variation for the set of maize hybrids} 
\begin{tabular}{rllllll}
  \toprule
 & DMY & DMC & FAT & PRO & STA & SUG \\ 
  \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: FALSE}}\\
T & 0.75 (0.0552) & 0.34 (0.0619) & 0.4 (0.0412) & 0.47 (0.0293) & 0.16 (0.0496) & 0.27 (0.1447) \\ 
  P & 0.54 (0.0493) & 0.48 (0.0521) & 0.21 (0.0365) & 0.6 (0.0187) & 0.35 (0.0427) & 0.42 (0.117) \\ 
  G & 0.74 (0.0517) & 0.63 (0.0521) & 0.43 (0.0356) & 0.65 (0.0223) & 0.46 (0.0458) & 0.47 (0.1261) \\ 
  PG & 0.71 (0.054) & 0.57 (0.0545) & 0.35 (0.0375) & 0.62 (0.0235) & 0.39 (0.0478) & 0.42 (0.1298) \\ 
  PT & 0.73 (0.056) & 0.53 (0.0594) & 0.35 (0.0398) & 0.61 (0.0254) & 0.31 (0.0504) & 0.37 (0.1396) \\ 
  GT & 0.75 (0.0533) & 0.61 (0.0553) & 0.43 (0.0374) & 0.65 (0.0239) & 0.44 (0.048) & 0.44 (0.1342) \\ 
   \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: TRUE}}\\
P & 0.46 (0.0469) & 0.53 (0.05) & 0.23 (0.0368) & 0.46 (0.0234) & 0.38 (0.0391) & 0.34 (0.1316) \\ 
  G & 0.67 (0.0534) & 0.47 (0.0552) & 0.43 (0.0384) & 0.48 (0.027) & 0.36 (0.0457) & 0.35 (0.132) \\ 
   \bottomrule
\multicolumn{6}{l}{}\\
\end{tabular}
\end{table}

% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Wed Mar 15 17:36:40 2017
% Script: ./analysis/maizego_core_fraction_plot_predictive_abilities.R
\begin{table}[ht]
\centering
\caption{Predictive abilities and corresponding coefficients of variation for different core sets from the tropical/subtropical material of the maize diversity panel.} 
\begin{tabular}{rllllll}
  \toprule
 & 100grainweight & cobweight & Eardiameter & Kernelwidth & Plantheight & Silkingtime \\ 
  \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: FALSE}}\\
G & 0.43 (0.0733) & 0.37 (0.1734) & 0.39 (0.0535) & 0.34 (0.0455) & 0.45 (0.0755) & 0.53 (0.0297) \\ 
  GT & 0.44 (0.0748) & 0.33 (0.1727) & 0.4 (0.0543) & 0.34 (0.0425) & 0.4 (0.0707) & 0.53 (0.0285) \\ 
   \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: TRUE}}\\
G\_1.0 & 0.36 (0.0773) & 0.21 (0.1678) & 0.3 (0.0527) & 0.34 (0.0472) & 0.41 (0.078) & 0.45 (0.0302) \\ 
  GT\_0.3 & 0.36 (0.0711) & 0.2 (0.1566) & 0.28 (0.0503) & 0.37 (0.044) & 0.42 (0.0736) & 0.5 (0.028) \\ 
  GT\_0.4 & 0.39 (0.0697) & 0.2 (0.1558) & 0.33 (0.0486) & 0.35 (0.0428) & 0.38 (0.0727) & 0.52 (0.028) \\ 
  GT\_0.5 & 0.41 (0.0671) & 0.16 (0.1549) & 0.31 (0.0486) & 0.4 (0.0414) & 0.44 (0.0748) & 0.49 (0.0278) \\ 
  GT\_0.6 & 0.4 (0.0739) & 0.13 (0.1563) & 0.27 (0.0497) & 0.37 (0.0417) & 0.42 (0.075) & 0.55 (0.0272) \\ 
  GT\_0.7 & 0.37 (0.0734) & 0.1 (0.1555) & 0.31 (0.0508) & 0.37 (0.0422) & 0.33 (0.0755) & 0.52 (0.028) \\ 
  GT\_0.8 & 0.4 (0.0774) & 0.21 (0.1581) & 0.36 (0.0515) & 0.41 (0.0458) & 0.29 (0.0737) & 0.49 (0.0288) \\ 
  GT\_0.9 & 0.39 (0.0792) & 0.21 (0.1692) & 0.38 (0.0561) & 0.41 (0.0459) & 0.29 (0.075) & 0.49 (0.0311) \\ 
  T\_1.0 & 0.4 (0.0747) & 0.15 (0.1568) & 0.37 (0.0509) & 0.36 (0.0423) & 0.32 (0.0692) & 0.49 (0.0279) \\ 
   \bottomrule
\multicolumn{6}{l}{}\\
\end{tabular}
\end{table}

>>>>

% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Wed Mar 15 17:31:28 2017
% Script: ./analysis/maizego_plot_predictive_abilities.R
\begin{table}[ht]
\centering
\caption{Predictive abilities and corresponding coefficients of variation for the set of maize hybrids} 
\begin{tabular}{rllllll}
  \toprule
 & DMY & DMC & FAT & PRO & STA & SUG \\ 
  \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: FALSE}}\\
T & 0.75 (0.0552) & 0.34 (0.0619) & 0.4 (0.0412) & 0.47 (0.0293) & 0.16 (0.0496) & 0.27 (0.1447) \\ 
  P & 0.54 (0.0493) & 0.48 (0.0521) & 0.21 (0.0365) & 0.6 (0.0187) & 0.35 (0.0427) & 0.42 (0.117) \\ 
  G & 0.74 (0.0517) & 0.63 (0.0521) & 0.43 (0.0356) & 0.65 (0.0223) & 0.46 (0.0458) & 0.47 (0.1261) \\ 
  PG & 0.71 (0.054) & 0.57 (0.0545) & 0.35 (0.0375) & 0.62 (0.0235) & 0.39 (0.0478) & 0.42 (0.1298) \\ 
  PT & 0.73 (0.056) & 0.53 (0.0594) & 0.35 (0.0398) & 0.61 (0.0254) & 0.31 (0.0504) & 0.37 (0.1396) \\ 
  GT & 0.75 (0.0533) & 0.61 (0.0553) & 0.43 (0.0374) & 0.65 (0.0239) & 0.44 (0.048) & 0.44 (0.1342) \\ 
   \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: TRUE}}\\
P & 0.46 (0.0469) & 0.53 (0.05) & 0.23 (0.0368) & 0.46 (0.0234) & 0.38 (0.0391) & 0.34 (0.1316) \\ 
  G & 0.67 (0.0534) & 0.47 (0.0552) & 0.43 (0.0384) & 0.48 (0.027) & 0.36 (0.0457) & 0.35 (0.132) \\ 
   \bottomrule
\multicolumn{6}{l}{}\\
\end{tabular}
\end{table}

% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Thu Mar 16 08:16:30 2017
% Script: ./analysis/uhoh_plot_predictive_abilities.R
\begin{table}[ht]
\centering
\caption{Predictive abilities and corresponding coefficients of variation for the set of maize hybrids. As predictors, pedigree (P), genomic (G), transcriptomic (T) data and combinations thereof we used.} 
\begin{tabular}{rllllll}
  \toprule
 & DMY & DMC & FAT & PRO & STA & SUG \\ 
  \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: FALSE}}\\
P & 0.54 (0.049) & 0.48 (0.052) & 0.21 (0.037) & 0.6 (0.019) & 0.35 (0.043) & 0.42 (0.117) \\ 
  G & 0.74 (0.052) & 0.63 (0.052) & 0.43 (0.036) & 0.65 (0.022) & 0.46 (0.046) & 0.47 (0.126) \\ 
  PG & 0.71 (0.054) & 0.57 (0.055) & 0.35 (0.038) & 0.62 (0.023) & 0.39 (0.048) & 0.42 (0.13) \\ 
  PT & 0.73 (0.056) & 0.53 (0.059) & 0.35 (0.04) & 0.61 (0.025) & 0.31 (0.05) & 0.37 (0.14) \\ 
  GT & 0.75 (0.053) & 0.61 (0.055) & 0.43 (0.037) & 0.65 (0.024) & 0.44 (0.048) & 0.44 (0.134) \\ 
   \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: TRUE}}\\
T & 0.75 (0.055) & 0.34 (0.062) & 0.4 (0.041) & 0.47 (0.029) & 0.16 (0.05) & 0.27 (0.145) \\ 
  P & 0.46 (0.047) & 0.53 (0.05) & 0.23 (0.037) & 0.46 (0.023) & 0.38 (0.039) & 0.34 (0.132) \\ 
  G & 0.67 (0.053) & 0.47 (0.055) & 0.43 (0.038) & 0.48 (0.027) & 0.36 (0.046) & 0.35 (0.132) \\ 
   \bottomrule
\multicolumn{6}{l}{}\\
\end{tabular}
\end{table}

% latex table generated in R 3.3.3 by xtable 1.8-2 package
% Thu Mar 16 08:03:02 2017
% Script: ./analysis/maizego_core_fraction_plot_predictive_abilities.R
\begin{table}[ht]
\centering
\caption{Predictive abilities and corresponding coefficients of variation for different core sets from the tropical/subtropical material of the maize diversity panel. As predictors, genomic (G) data, transcriptomic (T) data and their combination (GT) were used. The decimal after the predictor name indicates the size of the genetic material that was covered by inbred lines in the core set.} 
\begin{tabular}{rllllll}
  \toprule
 & 100grainweight & cobweight & Eardiameter & Kernelwidth & Plantheight & Silkingtime \\ 
  \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: FALSE}}\\
G\_Full & 0.43 (0.0733) & 0.37 (0.1734) & 0.39 (0.0535) & 0.34 (0.0455) & 0.45 (0.0755) & 0.53 (0.0297) \\ 
  GT\_Full & 0.44 (0.0748) & 0.33 (0.1727) & 0.4 (0.0543) & 0.34 (0.0425) & 0.4 (0.0707) & 0.53 (0.0285) \\ 
   \midrule
\multicolumn{6}{l}{{\bfseries Only incomplete predictor: TRUE}}\\
G\_1.0 & 0.36 (0.0773) & 0.21 (0.1678) & 0.3 (0.0527) & 0.34 (0.0472) & 0.41 (0.078) & 0.45 (0.0302) \\ 
  T\_1.0 & 0.4 (0.0747) & 0.15 (0.1568) & 0.37 (0.0509) & 0.36 (0.0423) & 0.32 (0.0692) & 0.49 (0.0279) \\ 
  GT\_0.9 & 0.39 (0.0792) & 0.21 (0.1692) & 0.38 (0.0561) & 0.41 (0.0459) & 0.29 (0.075) & 0.49 (0.0311) \\ 
  GT\_0.8 & 0.4 (0.0774) & 0.21 (0.1581) & 0.36 (0.0515) & 0.41 (0.0458) & 0.29 (0.0737) & 0.49 (0.0288) \\ 
  GT\_0.7 & 0.37 (0.0734) & 0.1 (0.1555) & 0.31 (0.0508) & 0.37 (0.0422) & 0.33 (0.0755) & 0.52 (0.028) \\ 
  GT\_0.6 & 0.4 (0.0739) & 0.13 (0.1563) & 0.27 (0.0497) & 0.37 (0.0417) & 0.42 (0.075) & 0.55 (0.0272) \\ 
  GT\_0.5 & 0.41 (0.0671) & 0.16 (0.1549) & 0.31 (0.0486) & 0.4 (0.0414) & 0.44 (0.0748) & 0.49 (0.0278) \\ 
  GT\_0.4 & 0.39 (0.0697) & 0.2 (0.1558) & 0.33 (0.0486) & 0.35 (0.0428) & 0.38 (0.0727) & 0.52 (0.028) \\ 
  GT\_0.3 & 0.36 (0.0711) & 0.2 (0.1566) & 0.28 (0.0503) & 0.37 (0.044) & 0.42 (0.0736) & 0.5 (0.028) \\ 
   \bottomrule
\multicolumn{6}{l}{}\\
\end{tabular}
\end{table}
